\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{School of random department names} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge This is the title of the template report \\ \horrule{2pt} \\[0.5cm]

### 2018-05-17 Report/notes.tex
Modifications of the report document in an effort to improve readability.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LaTeX Example: Project Report
%
% Source: http://www.howtotex.com
%
% Feel free to distribute this example, but please keep the referral
% to howtotex.com
% Date: March 2011 
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% How to use writeLaTeX: 
%
% You edit the source code here on the left, and the preview on the
% right shows you the result within a few seconds.
%
% Bookmark this page and share the URL with your co-authors. They can
% edit at the same time!
%
% You can upload figures, bibliographies, custom classes and
% styles using the files menu.
%
% If you're new to LaTeX, the wikibook is a great place to start:
% http://en.wikibooks.org/wiki/LaTeX
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Edit the title below to update the display in My Documents
%\title{Project Report}
%
%%% Preamble
\documentclass[paper=a4, fontsize=11pt]{scrartcl}
\usepackage[T1]{fontenc}
\usepackage{fourier}

@@

	\section{Queue : A toy example}
	We considere a M/M/1/n queue (see Kendall notation).

@@

		\path (s0) edge [bend left]             node {Dirac(t)} (s1)
		(s1) edge [bend left] node {$\lambda$} (s0)
		edge  [bend left]            node {Dirac(t)} (s2)
		(s2) edge [bend left]             node {$\lambda$} (s1)
		edge [bend left]  node {Dirac(t)} (s3)
		(s3) edge [bend left]              node {$\lambda$} (s2)
		edge [bend left]  node {Dirac(t)} (s4)
		(s4) edge [bend left]             node {$\lambda$} (s3)
		edge [bend left]  node {Dirac(t)} (sw)
		(sw) edge [bend left]             node {$\lambda$} (s4)
		edge [bend left]  node {Dirac(t)} (sn)
		(sn) edge [bend left]             node {$\lambda$} (sw);
		\end{tikzpicture}
		\caption{Queue with n capacity, the current size is written on the states}
		\label{fig:Queue1}
	\end{figure}

@@

		\caption{Prism code for figure \ref{fig:Queue1}}
		\label{fig:queuecode1}
	\end{figure}

@@

		(s02)   edge   node {$\lambda$} (sw0)
		edge   node {$\mu$} (s03)
		(s03)   edge  node {$\lambda$} (sw0)
		edge   node {$\mu$} (s04)
		(s04) edge  node {$\lambda$} (sw0)
		edge   node {$\mu$} (s05)
		(s05) edge  node {$\lambda$} (sw0)
		edge   node {$\mu$} (s1)
		(s1)    edge  node {$\lambda$} (s0)
		edge   node {$\mu$} (s12)
		(s12)   edge  node {$\lambda$} (s0)
		edge   node {$\mu$} (s13)
		(s13) edge  node {$\lambda$} (s0)
		edge   node {$\mu$} (s14)
		(s14) edge  node {$\lambda$} (s0)
		edge   node {$\mu$} (s15)
		(s15) edge  node {$\lambda$} (s0)
		edge   node {$\mu$} (s2)
		(s2) edge  node {$\lambda$} (s1)
		edge   node {$\mu$} (sw1)    
		(sw1) edge  node {$\lambda$} (s1);
		\end{tikzpicture}
		\caption{Queue with phase type fitting of parameter k}
		\label{fig:queueptf1}
	\end{figure}

@@

		(s02)   edge   node {$\lambda$} (sw02)
		edge   node {$\mu$} (s03)
		(s03)   edge  node {$\lambda$} (sw03)
		edge   node {$\mu$} (s04)
		(s04) edge  node {$\lambda$} (sw04)
		edge   node {$\mu$} (s05)
		(s05) edge  node {$\lambda$} (sw05)
		edge   node {$\mu$} (s1)
		(s1)    edge  node {$\lambda$} (s0)
		edge   node {$\mu$} (s12)
		(s12)   edge  node {$\lambda$} (s02)
		edge   node {$\mu$} (s13)
		(s13) edge  node {$\lambda$} (s03)
		edge   node {$\mu$} (s14)
		(s14) edge  node {$\lambda$} (s04)
		edge   node {$\mu$} (s15)
		(s15) edge  node {$\lambda$} (s05)
		edge   node {$\mu$} (s2)
		(s2) edge  node {$\lambda$} (s1)
		edge   node {$\mu$} (sw1)    
		(sw1) edge  node {$\lambda$} (s12);
		\end{tikzpicture}
		\caption{Queue with phase type fitting of parameter k}
		\label{fig:queueptf2}
	\end{figure}

@@

		\end{lstlisting}
		\caption{Caption}
		\label{fig:queuecode2}
	\end{figure}

@@

	\begin{figure}
		\centering
		\includegraphics[width=18cm]{sspqueue.png}
		\caption{The blue line is the result without phase type fitting}
		\label{fig:res1}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=16cm]{time.png}
		\caption{time of computation versus k}
		\label{fig:time1}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=16cm]{size.png}
		\caption{size of model versus k}
		\label{fig:time1}
	\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LaTeX Example: Project Report
%
% Source: http://www.howtotex.com
%
% Feel free to distribute this example, but please keep the referral
% to howtotex.com
% Date: March 2011 
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% How to use writeLaTeX: 
%
% You edit the source code here on the left, and the preview on the
% right shows you the result within a few seconds.
%
% Bookmark this page and share the URL with your co-authors. They can
% edit at the same time!
%
% You can upload figures, bibliographies, custom classes and
% styles using the files menu.
%
% If you're new to LaTeX, the wikibook is a great place to start:
% http://en.wikibooks.org/wiki/LaTeX
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Edit the title below to update the display in My Documents
%\title{Project Report}
%
%%% Preamble
\documentclass[paper=a4, fontsize=11pt]{scrartcl}
\usepackage[T1]{fontenc}
\usepackage{fourier}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links 
    urlcolor=cyan           % color of external links
}

@@

	\section{Queue : A toy example}
	We consider a D/M/1/n queue.

@@

		\path (s0) edge [bend left]             node {Dirac(t)} (s1)
		(s1) edge [bend left] node {$\lambda$} (s0)
		edge  [bend left]            node {Dirac(t)} (s2)
		(s2) edge [bend left]             node {$\lambda$} (s1)
		edge [bend left]  node {Dirac(t)} (s3)
		(s3) edge [bend left]              node {$\lambda$} (s2)
		edge [bend left]  node {Dirac(t)} (s4)
		(s4) edge [bend left]             node {$\lambda$} (s3)
		edge [bend left]  node {Dirac(t)} (sw)
		(sw) edge [bend left]             node {$\lambda$} (s4)
		edge [bend left]  node {Dirac(t)} (sn)
		(sn) edge [bend left]             node {$\lambda$} (sw);
		\end{tikzpicture}
		\caption{D/M/1/n queue with capacity $n$. The Dirac-distributed arrival event does not reset when the exponential service event occurs.}
		\label{fig:Queue1}
	\end{figure}

@@

		\caption{PRISM GSMP model of a D/M/1/n queue as shown in \ref{fig:Queue1}.}
		\label{fig:queuecode1}
	\end{figure}

@@

		(s02)   edge   node {$\lambda$} (sw0)
		edge   node {$\mu$} (s03)
		(s03)   edge  node {$\lambda$} (sw0)
		edge   node {$\mu$} (s04)
		(s04) edge  node {$\lambda$} (sw0)
		edge   node {$\mu$} (s05)
		(s05) edge  node {$\lambda$} (sw0)
		edge   node {$\mu$} (s1)
		(s1)    edge  node {$\lambda$} (s0)
		edge   node {$\mu$} (s12)
		(s12)   edge  node {$\lambda$} (s0)
		edge   node {$\mu$} (s13)
		(s13) edge  node {$\lambda$} (s0)
		edge   node {$\mu$} (s14)
		(s14) edge  node {$\lambda$} (s0)
		edge   node {$\mu$} (s15)
		(s15) edge  node {$\lambda$} (s0)
		edge   node {$\mu$} (s2)
		(s2) edge  node {$\lambda$} (s1)
		edge   node {$\mu$} (sw1)    
		(sw1) edge  node {$\lambda$} (s1);
		\end{tikzpicture}
		\caption{Queue with phase type fitting of parameter k.}
		\label{fig:queueptf1}
	\end{figure}

@@

		(s02)   edge   node {$\lambda$} (sw02)
		edge   node {$\mu$} (s03)
		(s03)   edge  node {$\lambda$} (sw03)
		edge   node {$\mu$} (s04)
		(s04) edge  node {$\lambda$} (sw04)
		edge   node {$\mu$} (s05)
		(s05) edge  node {$\lambda$} (sw05)
		edge   node {$\mu$} (s1)
		(s1)    edge  node {$\lambda$} (s0)
		edge   node {$\mu$} (s12)
		(s12)   edge  node {$\lambda$} (s02)
		edge   node {$\mu$} (s13)
		(s13) edge  node {$\lambda$} (s03)
		edge   node {$\mu$} (s14)
		(s14) edge  node {$\lambda$} (s04)
		edge   node {$\mu$} (s15)
		(s15) edge  node {$\lambda$} (s05)
		edge   node {$\mu$} (s2)
		(s2) edge  node {$\lambda$} (s1)
		edge   node {$\mu$} (sw1)    
		(sw1) edge  node {$\lambda$} (s12);
		\end{tikzpicture}
		\caption{Queue with phase type fitting of parameter k.}
		\label{fig:queueptf2}
	\end{figure}

@@

		\end{lstlisting}
		\caption{PRISM CTMC model of the D/M/1/n queue as shown in \ref{fig:Queue1} with phase-type fitting to approximate the deterministic arrivals. The phase-type module \emph{trigger} is used as suggested on the \href{http://www.prismmodelchecker.org/manual/FrequentlyAskedQuestions/PRISMModelling}{PRISM website}.  }
		\label{fig:queuecode2}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=12cm]{faq-erlang.jpg}
		\caption{The effect of $k$, the number of time points within the sequence of exponential transitions, on the shape of the resulting phase-type distribution. Increasing $k$ makes the phase-type distribution more deterministic. This picture was taken from the \href{http://www.prismmodelchecker.org/manual/FrequentlyAskedQuestions/PRISMModelling}{PRISM website}.}
		\label{fig:time1}
	\end{figure}

@@

	\begin{figure}
		\centering
		\includegraphics[width=18cm]{sspqueue.png}
		\caption{The blue line is the result without phase type fitting.}
		\label{fig:res1}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=16cm]{time.png}
		\caption{Computation time for different values of $k$. The growing lines represent computations of models with phase-type distributions. For about $k>200$, GSMP implementation starts outperforming all phase-typed computations, despite the GSMP implementation being relatively poorly optimized.}
		\label{fig:time1}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=16cm]{size.png}
		\caption{Size of model for different values of $k$.}
		\label{fig:time1}
	\end{figure}
